---
title: "Getting Started with dieroll"
author: "Huiqing Fu"
date: `r Sys.Date()`
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction to dieroll}      %\VignetteEngine{knitr::rmarkdown}               %\VignetteEncoding{UTF-8}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(collapse = T, comment = "#>")
library(dieroll)
```

## Die Rolling
The package `"dieroll"` is a minimal implementation for simulating rolling a die a given number of times, and to visualize the relative frequencies in such a series of rolls.

##Creating a die
The first step is to create a `"die"` object with the function `roll()`:    
```{r}
mydie <- die()
mydie
```
By default, die() creates a fair die with standard sides of 6, and with probability values for each side of 1/6.    
You can change the defatuls with arguments `sides` and `prob`:
```{r}
load <- die(sides = 1:6, prob = c(0.2,0.2,0.1,0.2,0.2,0.1))
load
```
##Tossing a coin
Once you have defined a "die" object, you can use the function `roll()` to roll a die a given number of times. The output will be an object of class "roll", which will contain the vector of `rolls`:
```{r}
roll100 <- roll(mydie, time = 100)
roll100
```
The `summary()` function gives you a nice table of frequencies:
```{r}
summary(roll100)
```
##Plot of relative frequencies
You can use the function `plot()` to create a graphic with the relative frequencies of a series of die rolls:
```{r}
plot(roll100)
```



